---
title: "EpiTxDb.Sc.sacCer3: Annotation package for EpiTxDb objects"
author: "Felix G.M. Ernst"
date: "`r Sys.Date()`"
package: EpiTxDb.Sc.sacCer3
output:
  BiocStyle::html_document:
    toc: true
    toc_float: true
    df_print: paged
vignette: >
  %\VignetteIndexEntry{EpiTxDb.Sc.sacCer3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: references.bib
---

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown(css.files = c('custom.css'))
```

# Available resources

`EpiTxDb.Sc.sacCer3` contains post-transcriptional RNA modifications from RMBase
v2.0 [[@Xuan.2017]](#References) and tRNAdb [[@Juehling.2009]](#References) and
can be accessed through the functions `EpiTxDb.Sc.sacCer3.tRNAdb()` and
`EpiTxDb.Sc.sacCer3.RMBase()`

```{r, echo=FALSE}
suppressPackageStartupMessages({
  library(EpiTxDb.Sc.sacCer3)
})
```
```{r, eval=FALSE}
library(EpiTxDb.Sc.sacCer3)
```
```{r}
etdb <- EpiTxDb.Sc.sacCer3.tRNAdb()
etdb
```

Modification information can be accessed through the typical function for an
`EpiTxDb` object, for example `modifications()`:

```{r}
modifications(etdb)
```

For a more detailed overview and explanation of the functionality of the 
`EpiTxDb` class, have a look at the `EpiTxDb` package.

# Sessioninfo

```{r}
sessionInfo()
```

<a name="References"></a>

# References
